mouse level quality plots

### 2020-01-10 doc/MouseLevelPlots.Rmd
Changed Mouse Level plots to show ALL mice (use original.DF instead of MLH1_data)

#load main data file
load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.5.20.RData")#added batch18
#load(file="data/MLH1/MLH1_data_setup_11.12.19.RData")#added batch17
#load(file="data/MLH1/MLH1_data_setup_9.26.19.RData")#added batch16
#load(file="data/MLH1/MLH1_data_setup_8.29.19.RData")#batch15 isn't showing up
#load(file="data/MetaData.RData")#this Rdata was replacing the most current batch.. agg!

@@

#remove other!
MLH1_data <- MLH1_data[MLH1_data$strain != "other",]

MLH1_data <- droplevels(MLH1_data)
```

@@

Yellow colored boxes are mice that will be exclude from the final (HQ) dataset for low quality cells (5). Consider re-runing this with the final data frame to see how the strain and mouse means change.

@@

#this loop makes a quant_status col for a list of mice (THERE'S AN ARGUMENT FOR Drawing a box around the mouse blocks )
#switch this loop to ex
for(i in 1:length(MLH1_data$mouse)){
  MLH1_data$quant_status[i] <- ifelse( is.element(MLH1_data$mouse[i], exclude_mice), "exclude", NA)
}

@@

df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
#this is where you remove the non-data data!
df_list <- df_list[ -c(24, 29) ]

@@

#make a new empty df. create a ddply thing with mean calculations (this is like a list for matching up later)
for(i in 1:(length(df_list))){
 # only include data with quality values, then create a ddply for specific sub-df that calqs mean by each mouse
  df_list[[i]] <- df_list[[i]][!(is.na(df_list[[i]]$quality) | df_list[[i]]$quality==""), ]
  sub_mouse_means <- ddply(df_list[[i]], .(mouse), summarise,
                      mouse_nMLH1 = mean(adj_nMLH1.foci)
  )
# this loop is going though each row of dataframes within the df.list and assigning the mouse mean
  for(o in 1:length(df_list[[i]]$Original.Name)){
    df_list[[i]]$mouse_mean_MLH1[o] <- sub_mouse_means$mouse_nMLH1[ (df_list[[i]]$mouse[o] == sub_mouse_means$mouse) ]
        }
}

plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(data = df_list[[h]], aes(colour = factor(Batch)), width = 0.25)+ 
    geom_jitter(aes(y= adj_nMLH1.foci, x= quality)) + xlim(c(0.5,5.5))+

@@

      geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
  #theme(plot.background = element_rect(fill = "green")) #theme for indiviual mice, 
  #make an empty ggplot? for missing data

>>>>

#load main data file

load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.10.20.RData")#edits to OG.original.DF
#load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.5.20.RData")#added batch18
#load(file="data/MLH1/MLH1_data_setup_11.12.19.RData")#added batch17
#load(file="data/MLH1/MLH1_data_setup_9.26.19.RData")#added batch16
#load(file="data/MLH1/MLH1_data_setup_8.29.19.RData")#batch15 isn't showing up
#load(file="data/MetaData.RData")#this Rdata was replacing the most current batch.. agg!

@@

#main data frame should be original_DF then changes made to MLH1_data

#remove other!
original_DF <- original_DF[original_DF$strain != "other",]

original_DF <- droplevels(original_DF)
```

```{r clean.OG.DF, echo=FALSE}
#because I want to display the MLH1 means from the OG list
#Have have to do a bit of clean up

#for this doc / report, remove 'X's (these changes to the DF won't be passed on)
original_DF <- original_DF[ !grepl("X", original_DF$X) , ]
original_DF <- original_DF[!(is.na(original_DF$nMLH1.foci) | original_DF$nMLH1.foci==""), ]

original_DF <- original_DF[!(is.na(original_DF$n) | original_DF$n != 20), ]

original_DF <- original_DF[original_DF$nMLH1.foci != "X",]
original_DF <- original_DF[original_DF$nMLH1.foci != "x",]

#
original_DF$n <- as.character(original_DF$n)
original_DF$nMLH1.foci<- as.character(original_DF$nMLH1.foci)
original_DF$quality<- as.character(original_DF$quality)

#remove non-number chrs
original_DF$n <- as.numeric(original_DF$n)
original_DF$nMLH1.foci<- as.numeric(original_DF$nMLH1.foci)
original_DF$quality<- as.numeric(original_DF$quality)

#when first ran there were alot of empty mouse -squares

original_DF <- droplevels(original_DF)

#num are nums, there are still Q5 cells
```

@@

The main data frame for these results is original_Df, which is a step removed from the final analysis DF. All of the mice of the data set are shown, to give a better idea of what is take out for the analysis dataset. ('X' labeled cells have been removed, Q5 cells remain).

Yellow colored boxes are mice that will be exclude from the final (HQ) dataset for low quality cells (5).

@@

#this loop makes a quant_status col for a list of mice (THERE'S AN ARGUMENT FOR Drawing a box around the mouse blocks )
#switch this loop to ex

#shouldn't the DF be the OG DF?

for(i in 1:length(original_DF$mouse)){
  original_DF$quant_status[i] <- ifelse( is.element(original_DF$mouse[i], exclude_mice_list), "exclude", NA)
}

@@

df_list <- split(original_DF, (original_DF$category))
#remove sections which are in category but have no data
#this is where you remove the non-data data!
df_list <- df_list[ -c(24, 29) ]

@@

#make a new empty df. create a ddply thing with mean calculations (this is like a list for matching up later)
for(i in 1:(length(df_list))){
 # only include data with quality values, then create a ddply for specific sub-df that calqs mean by each mouse
  df_list[[i]] <- df_list[[i]][!(is.na(df_list[[i]]$quality) | df_list[[i]]$quality==""), ]
  sub_mouse_means <- ddply(df_list[[i]], .(mouse), summarise,
                      mouse_nMLH1 = mean(nMLH1.foci)
  )
# this loop is going though each row of dataframes within the df.list and assigning the mouse mean
  for(o in 1:length(df_list[[i]]$Original.Name)){
    df_list[[i]]$mouse_mean_MLH1[o] <- sub_mouse_means$mouse_nMLH1[ (df_list[[i]]$mouse[o] == sub_mouse_means$mouse) ]
        }
}

plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(data = df_list[[h]], aes(colour = factor(Batch)), width = 0.25)+ 
    geom_jitter(aes(y= nMLH1.foci, x= quality)) + xlim(c(0.5,5.5))+

@@

      geom_hline(yintercept = c( mean(df_list[[h]]$nMLH1.foci) ), color="black" )
  #theme(plot.background = element_rect(fill = "green")) #theme for indiviual mice, 
  #make an empty ggplot? for missing data
